\documentclass[12pt,a4paper]{moderncv}
\usepackage{palatino}


\moderncvstyle{casual}
\moderncvcolor{blue}  
\usepackage{graphicx} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage[margin=2cm, headheight=15pt]{geometry}
\fontsize{24}{16}\selectfont


\name{Jiajun}{Zhang}
\title{Curriculum Vitae}
\address{}
\phone[mobile]{+1~(438)~351~3339}
\email{zhangjohnson729@gmail.com}


\begin{document}
\makecvtitle

\section{Education}
\cventry{2022--2026}{Bachelor of Science}{McGill University}{Honors Applied Mathematics}{}{$\bullet$ Overall GPA in Mathematics Courses : 3.78 
%$\bullet$ IELTS Test Score (Taken in summer 2021) : Overall 7.0 (Listening 7.0, Reading 6.5, Writing 6.5, Speaking 7.0) \\
%$\bullet$ GRE Test Score (Taken in April 2025) : 
}



\section{Experience}
\cventry{2023.9--Present}{Personal Math Tutor}{McGill University}{}{}{I work as a personal tutor under the peer-tutoring program offered by McGill University (Supervisor : \textit{Pavlina Pajot}). I will hold in-person tutoring sessions with one or more students upon demand.}

\cventry{2023.9--2024.4}{Undergraduate Course Assistant}{McGill University}{}{}{The course I am responsible for is MATH 223 Linear Algebra (Supervisor:  \textit{Mikael Pichot} ) at McGill University. This is a 
job for grading students' homework and also writing 
solutions, and answering students' questions.}

\cventry{2023.9--2024.4}{Software Engineer}{McGill University}{McGill Robotics Club}{}{I am a member at McGill Robotics Club for one year, during this time I work under the drone project as a software engineer. I mainly use C++ and Python to work with drone's vision systems.}


\cventry{2024.9--2024.12}{Undergraduate Course Assistant}{McGill University}{}{}{The course I am responsible for is Math 248 Honours Vector Calculus (Supervisor:  \textit{Jean-Pierre Mutanguha}) at McGill University. This is a job for grading students' homework and also writing solutions, and answering students' questions via the discussion board.}

\cventry{2024.9--2025.4}{Math Tutor at Math Help Desk}{McGill University}{}{}{I work as a math tutor at Burnside Building 911 (Supervisor : \textit{Jerome Fortier}). This position is aimed for answering students' questions from a wide variety of math courses which they are having troubles with, including calculus, linear algebra, abstract algebra, analysis, probability and statistics, ODE and PDE. I will hold weekly office hours and will answer questions from students that are present.}

\section{Projects}
\cventry{2022.9--Present}{My LaTeX Notes for Undergraduate Courses}{McGill University}{}{}{During my undergraduate degree, I use LaTeX to write the notes for core mathematics courses, those include calculus, linear algebra, abstract algebra, real analysis, measure theory, point-set topology, ODE, PDE, probability, statistics, differential geometry and more (some notes are still under construction). The latest PDF version of those can be found here :}




\end{document}
