\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath, amssymb, amsthm}

\usepackage[margin=2cm, headheight=15pt]{geometry}
\fontsize{24}{16}\selectfont
\setlength{\parindent}{0pt}
\usepackage{esdiff}
\usepackage{fixdif}
\usepackage{hyperref}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\Span}{span}
\usepackage{xcolor}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\kernel}{Ker}
\DeclareMathOperator{\image}{Im}
\DeclareMathOperator{\intd}{d}
\DeclareMathOperator{\trace}{tr}
\usepackage{fancyhdr}
\fancyhf{}

\begin{document}

\begin{center}
    \resizebox{!}{1em}{\textbf{Jiajun Zhang}}
    
    
    \hrulefill
    \vspace*{0.2cm}
    
    \textbf{\textit{zhangjohnson729@gmail.com | 438-351-3339 | GitHub : JohanssonRein}}
\end{center}

\vspace*{0.3cm}
\textbf{WORKING EXPERIENCES}

\vspace*{0.3cm}
$\bullet$ (2023 Fall - 2024 Winter) Undergraduate 
Teaching Assistant (MATH 133 Linear Algebra and 

\hspace*{0.25cm}
Geometry), McGill University. This is a 
job for grading students' homework and also writing 

\hspace*{0.25cm}
solutions, and answer students' questions.

\vspace*{0.2cm}
$\bullet$ (2024 Winter - 2024 Summer) Undergraduate 
Teaching Assistant (MATH 223 Linear Algebra),  

\hspace*{0.25cm}
McGill University. This is a job for grading students' homeworks and
also writing solutions.

\vspace*{0.2cm}
$\bullet$ (2023 Fall - 2024 Fall) Undergraduate Math Tutor, 
McGill University. This position is aimed at 

\hspace*{0.2cm}
helping students 
with math difficulties and provide tutorials to them.


\vspace*{0.3cm}
\textbf{VOLUNTEERING EXPERIENCES}

\vspace*{0.3cm}
$\bullet$ (2023 Fall - Current) McGill Robotics Club, Drone 
Project, Software Team 


$\bullet$ (2023 October) McGill Competetive Programming's 
Hackathon, ranked 14 out of 45 teams

\vspace*{0.3cm}
\textbf{PROJECTS}

\vspace*{0.3cm}
$\bullet$ \textbf{Civilization 250 : } Object Oriented Programming in Java,
involves classes, constructors, fields, 

\hspace*{0.25cm} inheritances.
\href{ https://github.com/JohanssonRein/Java-Project-1}{\textbf{\textcolor{red}{\textit{GitHub Link Here}}}}
\textit{ https://github.com/JohanssonRein/Java-Project-1}

\vspace*{0.2cm}
$\bullet$ \textbf{Caterplliar Game :} Linked Lists in Java, 
involves traversal and Object Oriented Programming.

\hspace*{0.25cm}
\href{ https://github.com/JohanssonRein/Java-Project-2}{\textbf{\textcolor{red}{\textit{GitHub Link Here}}}}
\textit{ https://github.com/JohanssonRein/Java-Project-2}

\vspace*{0.2cm}
$\bullet$ \textbf{Decision Tree :} Tree Traversals in Java, involves
large database, decision tree, machine learning.

\hspace*{0.25cm}
\href{ https://github.com/JohanssonRein/Java-Project-3}{\textbf{\textcolor{red}{\textit{GitHub Link Here}}}}
\textit{ https://github.com/JohanssonRein/Java-Project-3}

\vspace*{0.2cm}
$\bullet$ \textbf{Survival Game :} Graphs, 
involves graph traversal like BFS and DFS, and algorithms like 

\hspace*{0.25cm}
Dijkstra's algorithm
\href{ https://github.com/JohanssonRein/Java-Project-4}{\textbf{\textcolor{red}{\textit{GitHub Link Here}}}}
\textit{ https://github.com/JohanssonRein/Java-Project-4}

\vspace*{0.2cm}
$\bullet$ \textbf{Python GUI :} A basic python GUI used in 
ROS to interact with robots, inside Ubuntu virtual 
\hspace*{0.25cm}
machine.
\href{https://github.com/JohanssonRein/ROS-Robotics}{\textbf{\textcolor{red}{\textit{GitHub Link Here}}}}
\textit{https://github.com/JohanssonRein/ROS-Robotics}

\vspace*{0.2cm}
$\bullet$ \textbf{Latex Source Code :} This repo contains all
my \LaTeX  work (source code + pdf) during my 

\hspace*{0.2cm}
unversity degree. 
\href{https://github.com/JohanssonRein/Latex-Source-Code}{\textbf{\textcolor{red}{\textit{GitHub Link Here}}}}
\textit{https://github.com/JohanssonRein/Latex-Source-Code}


\vspace*{0.3cm}
\textbf{SKILLS}

\vspace*{0.3cm}
$\bullet$ \textbf{Technical Skills : } Java, Python, C, OCaml, Bash / Mirosoft Excel, Word, Powerpoint

$\bullet$ \textbf{Developer Skills : } Github, VS Code, Intellij, \LaTeX, MatLab

$\bullet$ \textbf{Personal Hobbies : } Curling, Badminton, Drawing, Cooking

$\bullet$ \textbf{Language Skills : } Proficiency in English and Mandarin


\vspace*{0.3cm}
\textbf{EDUCATION}

\vspace*{0.3cm}
$\bullet$ McGill University 2022 - 2026, 
Honors Statistics and Computer Science, Undergraduate, B. Sc

\vspace*{0.3cm}
\textbf{FIELDS OF INTERESTS}

\vspace*{0.3cm}
$\bullet$ Applied Machine Learning, Database, Statistics, 
AI






\end{document}